---
title: "wineNMR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(wineNMR)
```

## Wine NMR Multitask Prediction

Reading in the data:

```{r}
wine_data = load_wine('../data')
```

Create a map of all of the wines:

```{r, echo=FALSE}
plot(wine_data, plot_type = 'map')
```


Plot an example of the NMR:

```{r}
plot(wine_data)
```



Create a dendrogram of the samples of NMR using protoclust:

```{r}
plot(wine_data, plot_type = 'dendrogram')
```
Create a correlation plot of the response matrix:

```{r}
plot(wine_data, plot_type = 'correlation')
```
Run glmnet with the mgaussian family option (using an alpha of 0.5 for elastic net):

```{r}
# run glmnet
fit = fit_wine(wine_data)
```

The percent of the NMR features removed:

```{r}
fit$percent_removed
```
```{r}
plot(fit$fit)
```

Predicting a subset of the responses:

```{r}
pred_wine = predict(fit, wine_data, c('malicAcid', 'ethanol', 'GlucFruct'))
```


Plot of the responses predicted:

```{r}
plot(pred_wine)
```

```{r}
plot(pred_wine, resid_plot = T)
```

